---
title: "Introduction to the EBA rulebook"
author: "Eryk Walczak"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EBArulebook)
```

# EBA rulebook

## Load and clean the rulebook

```{r}
articles_df <- parse_EBA_page()
```

Show the results

```{r}
dplyr::glimpse(articles_df)
```

## Get the content of the single rulebook

Not working - dev

```{r, eval = FALSE}
######## DEVELOPMENT #######
ruleITS <-
  "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/811"
ruleQA <-
  "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/536"

rule <- xml2::read_html(ruleITS)
rule <- xml2::read_html(ruleQA)

# columns
a <- rule %>% html_nodes(".aui-w20") %>% html_text()
b <- rule %>% html_nodes(".aui-w80") %>% html_text()

c <- data.frame(Text = t(b))
colnames(c) <- a

# ITS
its <- rule %>% html_nodes(".ITS") %>% html_text
its_url <- rule %>%
  html_nodes(".ITS") %>%
  html_nodes("a") %>%
  html_attr("href") %>%
  paste0("https://eba.europa.eu", .) # TODO only add if blank
its_regulatory_paper_url <- paste0(its_url, "-/regulatory-activity/consultation-paper")

######################################

#### TODO: other selectors
## ITS + Q&A
its_qa_url <- "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/3606"
its_qa <- read_html(its_qa_url)
# text
its_qa %>% html_nodes(".ITSqa") %>% html_text()
# urls
its_qa %>% html_nodes(".ITSqa") %>% html_nodes("a") %>% html_attr("href")

# RTS
# e.g. "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/2420"
".RTS"

# RTS+QA
# e.g. "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/1502"
".RTSqa"

# GL - guidelines. there is a Consultation Paper when following the href in .GL
# e.g. "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/1682"
".GL"

# GL + Q&A / href
# e.g. "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/951"
".GLqa"

# DA + QA
# e.g. "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/1023"
".DAqa"

######################################

# Q&A
many_QAs_url <- "https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/2420"
rule <- read_html(many_QAs_url)
qa <- rule %>% html_nodes(".QandA") %>% html_text
qa_url <- rule %>%
  html_nodes(".QandA") %>%
  html_nodes("a") %>%
  html_attr("href") %>%
  paste0("https://eba.europa.eu", .) # TODO only add if blank

# Q&A content - use separate function. TODO: go through all QA URLs
# this scraper below works only when direct QA link is available (i.e. 'qna/view/')
# it will fail when more than 1 QA were submitted (e.g. 'qna/search')
qa_url_content_html <- read_html(qa_url)
qa_url_content_col1 <- qa_url_content_html %>% html_nodes(".aui-w25") %>% html_text
qa_url_content_col2 <- qa_url_content_html %>% html_nodes(".aui-w75") %>% html_text

# or scrape all Q&A - preferred option
# use headless browser to go through:
# "https://eba.europa.eu/single-rule-book-qa?p_p_id=questions_and_answers_WAR_questions_and_answersportlet&p_p_lifecycle=0&p_p_state=normal&p_p_mode=view&p_p_col_id=column-1&p_p_col_pos=1&p_p_col_count=2&_questions_and_answers_WAR_questions_and_answersportlet_jspPage=%2Fhtml%2Fview.jsp&_questions_and_answers_WAR_questions_and_answersportlet_viewTab=1&_questions_and_answers_WAR_questions_and_answersportlet_emptySearch=0&_questions_and_answers_WAR_questions_and_answersportlet_statusSearch=1&currentTab=All"
# then extract IDs > then get w25 and w75
```

## Get EBA rules

Default option is to load previously scraped rulebook

```{r}
all_eba_rules <- scrape_EBA()
```

Which returns clean data frame with the content of the single rulebook. Additional column showing if additional tags are available (e.g. Q&A or Technical Standards).

```{r}
dplyr::glimpse(all_eba_rules)
```

When the files are not available locally, the rulebook can be scraped (all rules)

```{r, eval = FALSE}
all_eba_rules <- purrr::map_df(articles_df$URL, scrape_EBA)
```

To scrape single rule

```{r, eval = FALSE}
scrape_EBA("https://eba.europa.eu/regulation-and-policy/single-rulebook/interactive-single-rulebook/-/interactive-single-rulebook/toc/504/article-id/601")
```

# Q&A

## Load parsed Q&As

Go to each URL to scrape the content of each Q&A

Use the javascript (phantomjs) scraper to pull dynamic pages which then get cleaned and scraped using rvest.

Once Q&As are scraped with phantomjs (output files, i.e. html pages, are provided in the /data folder), they need to be parsed to extract URLs of each Q&A.

```{r}
qa_total <- parse_EBA_QA_page()
```

Show the data frame. It contains a title and corresponding URL of each Q&A.

```{r}
dplyr::glimpse(qa_total)
```

## Get Q&As

The content of Q&As was saved locally to avoid scraping the EBA page each time

```{r}
qa_df <- scrape_EBA_QA()
```

This return a data frame with content of all Q&As

```{r}
dplyr::glimpse(qa_df)
```

Data frame contains all fields in contained in Q&As (see an [example](https://eba.europa.eu/single-rule-book-qa/-/qna/view/publicId/2019_4601)). Additionally, all hyperlinks available in the body (fields: **Question**, **Background** and **EBA answer**) were scraped and put into the **QA_links** column (e.g. [link](https://eba.europa.eu/regulation-and-policy/payment-services-and-electronic-money/regulatory-technical-standards-on-strong-customer-authentication-and-secure-communication-under-psd2) to **Commission Delegated Regulation (EU) 2018/389** in the given example).

### Scraping

To scrape single Q&A pass a URL ([qa_total$URL[1]](https://eba.europa.eu/single-rule-book-qa;jsessionid=34AB2726D35F823AAAF6534743340A6D?p_p_id=questions_and_answers_WAR_questions_and_answersportlet&p_p_lifecycle=0&p_p_state=normal&p_p_mode=view&p_p_col_id=column-1&p_p_col_pos=1&p_p_col_count=2&_questions_and_answers_WAR_questions_and_answersportlet_jspPage=%2Fhtml%2Fquestions%2Fviewquestion.jsp&_questions_and_answers_WAR_questions_and_answersportlet_viewTab=1&_questions_and_answers_WAR_questions_and_answersportlet_questionId=2638504&_questions_and_answers_WAR_questions_and_answersportlet_statusSearch=1))

```{r, eval = FALSE}
scrape_EBA_QA(qa_total$URL[1])
```

To scrape all Q&As

```{r, eval = FALSE}
qa_df <- purrr::map_df(qa_total$URL, scrape_EBA_QA)
```

# Technical Standards

## TODO turn into functions / remove Depends

```{r}
# TODO uncomment
```

